<<<<<<< HEAD
The purpose of the black box optimization was to find the best number of epochs and the best size of the training sets. It showed in both predictions --- wind power and electricity price --- what was expected of it. It revealed that too many or too few numbers of epochs resulted in an over- or under-fitting of the networks function. Section~\ref{sec:annSection} describes common pitfalls when using Artificial Neural Networks where the generalization function of the network is overfitted. In short the generalization function is fitted only to the training set and therefore not able to predict beyond it, i.e. predict the values in the testing set. In this thesis we have dealt with over-fitting by early stopping and dividing the datasets into a training set and a testing set. We tried different epochs from 1-2800 and selected the number of epochs that achieved the best result on the testing set. It gives the best picture since predictions will naturally be done on data that has not been seen before.
=======
The purpose of the black box optimization was to find the best number of epochs and best size of the training set. It showed in both predictions --- wind power and electricity price --- what was expected of it. It revealed that too many or too few number of epochs resulted in an over- or under-fitting of the networks function. Section~\ref{sec:annSection} describes common pitfalls when using Artificial Neural Networks where the generalization function of the network is overfitted. In short the generalization function is fitted only to the training set and therefore not able to predict beyond it, i.e. predict the values in the testing set. In this thesis we have dealt with over-fitting by early stopping and dividing the datasets into a training set and a testing set. We tried different epochs from 1-2800 and selected the number of epochs that achieved the best result on the testing set. It gives the best picture since predictions will naturally be done on data that has not been seen before. Furthermore, we have reduced the number of neurons through pruning to avoid interference with performance of the system as described in the common pitfalls of the Artificial Neural Networks Section~\ref{sec:ANNCommonPitfalls}.
>>>>>>> c4c64c269a113cc7983a7f9a5f606627a36a6793

Over- and under-training of the network as presented in\cite{1} were more clear for wind power. Too small and too large datasets resulted in a significant deterioration in the error from 19,7\% to 48,64\% compared to the best dataset size of 3 months (Section~\ref{sec:experimentFourBlackBox}). The same did not apply for the electricity price predictions where the best size showed to be half a year and where the errors were closer to the best result varying from 3,19\% to 7,19\% (Section~\ref{sec:priceExperimentFour}). It emphasizes the need for experimenting with the right amount for the specific type of prediction.

The purpose of the time measurements is to illustrate the impact of the training period which includes pruning, training and prediction of a whole year. The prediction time showed to be almost linear with the training set size in both cases. The times varied from 232 to 844 seconds for electricity prices and 462 to 1585 seconds for wind power when predicting an entire year. The difference between electricity price and wind power times are found in the use of two computers with different computational power. A time-consuming element in the predictions are the identification of the network structure through pruning and the actual training of the network before doing all day-ahead predictions --- this procedure is always done before the predictions. The beginning procedure accounts for about 1/20 of the time whereas the subsequent 360 predictions (one for each day of the year) is the rest. The best electricity price prediction took 397 seconds which would result in approximately 20 seconds (397/20) of pruning and training before being able to predict. The individual predictions only take seconds and in a real setting only one day is predicted at a time which makes the pruning and training the most significant time consumers --- the approximately 20 seconds of wait time and the few seconds it takes to predict makes it possible to use the Artificial Neural Network model makes it feasible for fast predictions of the hour to come. If time becomes an issue our results show the influence of computational power which can be considered and a better processor could be used as a solution to bring down the time to predict. The focus on the time perspective will have a more significant role if the algorithm was to be used in an autonomous trading system with the purpose of placing bids automatically.  

<<<<<<< HEAD
The best results from Section~\ref{sec:experimentFourBlackBox} and ~\ref{sec:priceExperimentFour} show how the results can be considered as robust and steady. The top five for wind power with different epochs vary from 121,02-125,96. For price the top five goes from 45,17-47,92. It emphasizes that the inputs and their representation influence the wind power and electricity price as seen throughout the previous experiments.
=======
The best results from Section~\ref{sec:experimentFourBlackBox} and ~\ref{sec:priceExperimentFour} show how the results can be considered as robust and steady. The top five for wind power with differet epochs vary from 121,02-125,96. For price the top five goes from 45,17-47,92. It emphasizes that the inputs and their representation influence the wind power and electricity price as seen throughout the previous experiments.
>>>>>>> c4c64c269a113cc7983a7f9a5f606627a36a6793
