\subsection{Input parameters}
The strength of the prediction is very much dependent on the quality of the underlying data. As described in Section~\ref{sec:dataCollection} the data must satisfy certain criteria before it can be used as input and output for the Feedforward Neural Network. It must be trustworthy and contain hourly observations for our specific purposes, e.g. day-ahead wind power and electricity price prediction based on a dataset that consists of hourly observations. All calculations in the ANN are based on this data which makes it of utmost importance for the forecast. The selection of the correct input parameters for testing is equally important which is described in the analysis in Chapter~\ref{ch:theANNs}. The analysis of both electricity price and wind production together with experiment one in Sections~\ref{sec:windPowerExperimentOne} and~\ref{sec:priceExperimentOne} show how the combination of the right parameters are the core to a good prediction. It is necessary to make a comprehensive analysis of the different parameters to know what to include in the experiments and how to represent the parameters. A good example of this is the seasonal aspect for electricity prices that showed a difference in the result when used as month or as the specific season (summer, winter, ect.). Consequently, the prerequisites for the wind power and electricity price experiments to perform accurately are the quality and selection of the input data since it is the basic foundation for the Feedforward Neural Network to generalize upon.

\cite{szkuta1999electricity,sansom1999neural,1} are examples of publications with limited information about the importance of analysing exactly what input parameters constitutes the electricity price in different markets, why and how they are represented (also discussed in Section~\ref{sec:priceExperimentThree}). A sensitivity test to identify influences have been carried out for 4 out of the 15 input in \cite{szkuta1999electricity} and there is no description of the last parameters. Article \cite{1} decided to use only historical price data for prediction but without going into detail with how it is represented. It makes it very difficult to imitate the behaviour and use or test their knowledge and experience on how to include and represent inputs the best possible way. The seasonal aspect can as mentioned be included in different forms for example can matrix be used and the combination of the inputs have very different impacts. Exactly what combination of inputs and how they are represented should always be documented for others to imitate and test on their own dataset so that the results can be compared based on the same data. Our experiments showed that even though some inputs were closely correlated to the output it was not necessarily included in the best prediction as seen with consumption and wind power in Section~\ref{sec:windPowerExperimentOne}. The black box nature of the ANN can identify unforeseen dependencies between the various input parameters. It is not enough to simply list the characteristics of the output to predict without mentioning what came out of the input analysis, if the experiments validated it and exactly what inputs were used for that particular market. The analysis is the foundation for what the experiments are supposed to validate, e.g. the hypotheses of experiment one are conducted based on the analysis. Expectations that was not met can also be explained by the analysis, for instance the substitution of consumption with air density or temperature. The influences of the electricity price can differ from country to country due to different markets and weather conditions. Therefore it must be included to make comparisons or feasibility studies between different markets possible. In \cite{sansom1999neural} the input analysis is described with the following statement:

\begin{quotation}
\textit{The 13 inputs to the neural network were selected by data analysis and by trial and error to produce the seven-day ahead electricity price forecast. The inputs were time, demand and price data obtained from the SEM web site...}
\end{quotation}

The focus should not be on results (MAE, MAPE) alone but also how the results are obtained through the dataset, especially in the case of input parameters for the neural network which has shown to be of utmost importance in our analysis. The point being that all publications use different datasets and experimental environments. In order to compare results to one another the different settings must be the same and tested on the same dataset. The lack in description of test environment and input analysis makes such comparisons difficult both due to the incomplete information but also because the format of the datasets cannot be seen or downloaded to extract the information. Comparison with another publication was attempted in Section~\ref{sec:priceExperimentThree} and it showed difficulties because we can never be certain of the experimental setup without it being properly documented --- it can be discussed if it is even fair. The purpose of our thesis is to identify the feasibility of an Feedforward Neural Network used for prediction of wind power and electricity prices. The above discussion is related to this topic because the feasibility of the ANN is directly dependent on the quality and transparency of the data that it generalizes upon. The analysis that identifies the correct inputs together with the experiments to verify the best combination and network configuration is the foundation for the result and in our experience the most time-consuming, i.e. the actual analysis and how to get from analysis to the best possible model. 

One thing to add is the differences between how wind power predictions is used in this thesis compared to other publications. They take as their starting point a physical windmill or wind-farm with all information about throughput of the mill(s)\cite{windForecastPortugal,ShortTermWindPowerForecasting,dayAheadImpactOfWindPowerForecasts,WindPowerGenerationUsingANN} whereas we try to predict the entire production for western Denmark (DK-1) based on the average weather conditions, demand and historical production data. The wind power was established to be related to the market through the co-relation to demand in Section~\ref{sec:consumptionWindProduction} but it is evident that wind power has more obvious core parameters than price. Wind will always have the most significant influence on wind power since it is what makes the blades go round whereas price will be more reliant on market forces. It does not change the need for analysing the specific conditions both because wind power is related to the market but also because the weather changes greatly from country to country, e.g. air density is much different in India~\ref{WindPowerGenerationUsingANN} and seasonality which was discarded in our experiments could play a more significant role in places with more significant changes in weather conditions than Denmark. The electricity price is also sensitive to external influences that can result in electricity price spikes\cite{singhal2011electricity}. These influences are only shortly mentioned but covers socio-cultural factors as described in Section~\ref{sec:ElectricityDemand} but also natural gas, oil, fuel prices and system loads\cite{singhal2011electricity}. Furthermore, the influence of holidays on demand are in our thesis included through the seasonality input but could have been modelled explicitly according to the actual calendar days. In \cite{EnergyPriceForecasting,chen2004load} they argue it is argued to have a significance on the price.

\subsection{Input combination}
As described above the different combinations of input parameters are found in experiment one for both electricity prices and wind power production. The experiments show the complexity in the black box nature of the ANN since it identifies better connections of input than foreseen. In wind power production the substitution of temperature and air density with consumption showed better accuracy which was not expected, whereas wind speed showed to be much more crucial to the electricity price than foreseen. Wind power production impacts the electricity price as presented in \cite{dayAheadImpactOfWindPowerForecasts} but more than expected through the wind speed. This leads to the potential of feeding the electricity price with the prediction of wind power as input instead of wind speed to make the prediction more accurate. This connection has to be investigated in future work.

The seasonality characteristic of the wind power production and electricity price time-series are in both cases significant and for that reason expected to increase performance for both predictions. Seasonality is reflected in the month input parameter and showed different results. The month parameter decreased the overall performance of the network in the case of wind power whereas it was increased in the electricity price. The first thought was the small size of the data only containing three months and therefore not reflecting the seasons from the previous year which was the intention. When attempted on a whole years training set it showed an overall worsening in accuracy due to over-training because of the bigger training set. The electricity prices with the seasonal aspect was also tried with a training set containing a year but as opposed to wind power the accuracy of the forecasts stayed the same. What can be concluded from this is that more data is not necessarily equal to better results in both cases. Three months of data is the most expressive for wind power and six months is the best for price. What was believed to be problematic was the shifting from one season to another where a new season was significantly different from the one we came from. This was proven wrong by the experiments for wind power since three months itself showed to contain enough information about the current season to be accurate. The electricity price also benefits from less data than a year with the dataset of six month. The the potential shortcomings from seasonal shifts were compensated by the omission of unnecessary data from the rest of the year. The high volatility results in many different cases during the year which can make it hard for the network to generalize when the data set becomes to large.

\subsection{Unseen data}
\label{sec:unseenDataDiscussion}
The wind power and electricity price experiments emphasized the need for measuring the accuracy of the results only on the testing set (unseen data). Section~\ref{sec:windPowerExperimentOne} highlights in Table~\ref{table:predictionMAEUnseenVsTrainingSet} how the MAE stays about the same for all predictions on the training set whereas a large difference is seen when applied on the testing set consisting of unseen data. Furthermore, different seasons and consumptions during the year result in many different days where the electricity prices and wind power behaves differently. This is also discussed in the analysis in Chapter~\ref{ch:theANNs} and therefore the experiments must as a minimum be performed on an entire year of unseen data to cover all possible scenarios and thereby reflect reality and to demonstrate how robust the prediction model is. All simulations in this thesis is performed once on a year but more testing on the same year could be conducted to further validate and strengthen results. This stands as opposed to the 5 weeks from different seasons used in \cite{1} which is argued to ensure fairness in results and reflect reality. \cite{pjmForecast} performs experiments on 5 different days of the entire year and then again on 2 weeks in February, i.e 19 days in total. Based on these days they conclude the following:

\begin{quotation}
\textit{The test results obtained through the simulation demonstrate that the proposed algorithm is robust, efficient, and accurate, and it produces better results for any day of the week.}
\end{quotation}

Omitting 340 days and concluding that it in general obtains better results is in direct contrast to our analysis of the seasonal aspect because the days differ much and also the results from experiment five in Section~\ref{sec:windPowerExperimentFive} and~\ref{sec:priceExperimentFive} where various starting points during the year greatly influences the overall results. The same omission of testing days applies for \cite{yamin2004adaptive} where a fixed testing period of one week is used for all experiments and at the same time is basis for their conclusion. According to our experiments a more comprehensive testing period must be taken into consideration due to the different days and different results when claiming the feasibility and sufficiency of the prediction which is also confirmed by \cite{forecastingSpotPricesAccountingForWindPower}. One good point to bring forward from \cite{yamin2004adaptive} is the discussion of the use of \fnurl{Monte Carlo method}{https://en.wikipedia.org/wiki/Monte_Carlo_method} to eliminate randomness by running the same experiments more than once. The ANN can give somewhat different results even though predicting the same days due to the weights being initialized randomly every time. The suggested method could be used in our experiments to strengthen the results. When testing the same results time constraints are likely to become an issue due to the large amount of tests already conducted. The way we try to eliminate randomness is by predicting an entire year so that all seasons are represented. Running the experiments more than once could be incorporated in such a way that an amount of the best predictions in every experiment could be run several times to ensure the results, e.g. running it several times for top-10 in every experiment to verify the order and the obtained MAE.
