Work in the field have established that an Artificial Neural Network handles time-series well that are non-linear, volatile and noisy (which applies for wind power and electricity prices) in an effective manner \cite{stockForecasting,pjmForecast,yamin2004adaptive,windForecastPortugal}. It is our intent to build on this experience and model Feedforward Neural Networks for prediction that uses the Resilient Backpropagation algorithm for training of the networks. In this dissertation we focus on utilizing the Feedforward Neural Networks for prediction of electricity prices and wind power by identifying the influential input parameters through a comprehensive analysis validated through experiments. Wind power and electricity price predictions are key instruments for decision making in the electricity market\cite{dayAheadImpactOfWindPowerForecasts,21} and the potential of Artificial Neural Networks for this purpose will be discussed.

Feedforward Neural Networks can be characterised as Machine Learning\cite{18} and historical data that is relevant for the specific task will be used for training. The goal is to investigate and identify (through analysis and experiments) the importance of the influential factors to be included and represented in these datasets. Based on this we examine the feasibility of a Resilient Backpropagation Feedforward Neural Network as a technology for predicting electricity prices and wind power. The feasibility will be examined by analysing the experimental results and the potential for practical use.
\\[0.5cm]
We will focus on; 1) identifying the influential factors for wind power and the electricity price; 2) modeling and implementing Feedforward Neural Networks with Resilient Backpropagation that are capable of predicting electricity price and wind power within the Danish electricity market; 3) evaluating predictions originating from the Artificial Neural Networks in terms of experimental results and decision making.