The rest of the thesis is structured as follows to uncover the presented hypotheses from Section~\ref{sec:theHypothesis}. 

\emph{Chapter 2, Main Concepts:} The chapter presents the main concepts within the area of wind power and electricity prediction. It includes a description of Machine Learning and Artificial Neural Networks that are used for prediction in this thesis. Different approaches to prediction of wind power and electricity prices have been presented and finally decision support is described. 

\emph{Chapter 3, Data Analysis:} A comprehensive analysis of the influential factors for wind power and electricity prices is conducted in this chapter. It includes description of the dataset and how it is collected together with the statistical tool to identify correlations between the influential factors and the output to predict.

\emph{Chapter 4, Forecasting Model:} The model used for prediction is presented here. The structure of the network, the training algorithm and the framework is described. Secondly, we point out strategies for our experiments with the network in order to identify the best approach to prediction of wind power and electricity price. 

\emph{Chapter 5, Experimental Results:} This chapter describes, analyses and concludes on the conducted experiments. The various experiments are based on the analysis and it has the purpose of rejecting or verifying the established hypotheses by simulating actual day-ahead predictions. The result of the chapter will be the best Artificial Neural Network models for electricity price and wind power (one for each) within the scope of the thesis.

\emph{Chapter 6, Experimental Result Discussion:} The experimental results is discussed here. The focus is to discuss the findings from Chapter 5 and simultaneously relate it to practical use (decision making) and other literature within the area of Artificial Neural Networks. It will be discussed here how the findings relate to the established hypotheses in the introduction.  

\emph{Chapter 7, Conclusion:} The results and findings of the thesis is concluded in this chapter.

\emph{Chapter 8, Appendix:} The appendix contains results and graphs from the experimental results.  
